COG-ED Manuscript

### 2021-12-09 06_Paper/COG-ED/Manuscript.Rmd

  rt <- data.frame(subject = character(), level = double(), meanrt = double())

@@

    meanrt <- mean(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                 +(levelindex[i]-1)], na.rm = TRUE)

    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
                          level = data_RT$level[levelindex[i]],
                          meanrt = meanrt)
    rt <- rbind(rt, newdata)

@@

      hypothesis1b_rmanova <- afex::aov_ez(data = h1b_data,
                                           dv = "meanrt",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)

>>>>

  rt <- data.frame(subject = character(), level = double(), medianrt = double())

@@

    medianrt <- median(data_RT$rt[which(data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1)
                                 +(levelindex[i]-1)], na.rm = TRUE)

    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
                          level = data_RT$level[levelindex[i]],
                          medianrt = medianrt)
    rt <- rbind(rt, newdata)

@@

      hypothesis1b_rmanova <- afex::aov_ez(data = h1b_data,
                                           dv = "medianrt",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)
